Statistical Stopping Criteria for Active Learning in Systematic Review Screening

### 2019-10-14 manuscript/main.tex
update minor mistakes in stopping criterion description

	Our aim is to formulate a stopping criterion such that a recall of $\tau$ has been reached with confidence level $\alpha$.
	To achieve this, we formulate a hypothesis test:
	We first calculate the number $\hat{n}$ of relevant documents that can maximally remain in the unseen documents to achieve a given recall target. The recall is defined as the ratio of seen relevant documents over all relevant documents
	\begin{equation}
		\tau = \frac{\hat{\rho}}{\rho + \tilde{n}}.
	\end{equation}
	Reorganization of this equation gives
	\begin{equation}
		\tilde{n} = \frac{\hat{\rho}}{\tau} - \rho.
	\end{equation}
	Because we need to use integers and want a conservative estimation, we are using the next largest integer given by the ceiling function:
	\begin{equation}
		\hat{n} = \lceil \frac{\rho}{\tau} - \hat{\rho} \rceil
	\end{equation}
	The null-hypothesis to reject can then be formulated as:
	\begin{quote}
	$H_0$: There are $\hat{n}$ or more relevant documents remaining in the set of unseen documents.
	\end{quote}

>>>>

	Our aim is to formulate a stopping criterion such that a recall of $\tau$ has been reached with confidence level $\alpha$.
	To achieve this, we formulate a hypothesis test:
	We first calculate the number $\hat{n}$ of relevant documents that can maximally remain in the unseen documents to achieve a given recall target. The recall is defined as the ratio of seen relevant documents over all relevant documents
	\begin{equation}
		\tau = \frac{\rho}{\hat{\rho} + \tilde{n}},
	\end{equation}
	with the number total number of seen relevant documents $\rho$, the number of seen relevant documents at the time we start random sampling $\hat{\rho}$, and the remaining number of relevant documents in the unseen sample at the time random sampling starts $\tilde{n}$.
	Reorganization of this equation gives
	\begin{equation}
		\tilde{n} = \frac{\rho}{\tau} - \hat{\rho}.
	\end{equation}
	Because we need to use integers, we get the next largest integer given by the ceiling function $\lceil \cdot \rceil$:
	\begin{equation}
		\hat{n} = \lceil \frac{\rho}{\tau} - \hat{\rho} \rceil
	\end{equation}
	The null-hypothesis to reject can then be formulated as:
	\begin{quote}
	$H_0$: There are $\hat{n}$ or more relevant documents remaining in the set of unseen documents.
	\end{quote}
